\chapter{Conclusion}\label{chapter:conclusion} 

In this thesis, the structure of winning tickets created with iterative magnitude pruning was analyzed empirically.
It was shown, that feed-forward neural networks consistently separated into two independent subnetworks by iterative magnitude pruning when trained on a dataset with independent tasks.
With the right conditions, such as a large enough network and enough pruning levels, the networks consistently separate over different pruning rates and network sizes.
The separation was tested on custom datasets with two independent tasks.
Systematic experiments were conducted on the Moons-Circles dataset, a simplistic toy dataset that contains two independent tasks.
Due to the success of the method on the toy task, experiments were also conducted on the `MNIST-Fashion-MNIST' dataset, which is significantly more realistic.
In both cases, neural networks were found to separate with non-trivial accuracy and without any regularization techniques.

These results indicate, that iterative magnitude pruning indeed produces winning tickets with meaningful structure.
Also, the results indicate that there is a probabilistic element to the degree to which these structures come to light.

\section{Limitations}
The findings of this thesis are empirical, and due the the scope and scale of the thesis, there are numerous untested scenarios.
The experiments were only conducted on toy datasets and on MNIST-Fashion-MNIST which might also be counted as a toy dataset.
Whether the findings remain true for larger and more realistic tasks remains an open question.

Another limitation is the restriction to datasets with similarly complex tasks.
Scenarios with tasks that vary in size or complexity were not tested in this thesis.
Further, only fully connected networks were tested.
Other architectures such as convolutional neural networks were not used in any experiments.
All of the limitations invite for future work on this topic.

\section{Discussion}
The experiments in this thesis demonstrate that iterative magnitude pruning finds independent subnetworks.
This can be valuable for understanding what the structure of winning tickets represents.
Further, it could also be valuable for machine learning interpretability.
A winning ticket could be trained and if independent networks occur, it could hint at independence in the dataset.
The same might be true for other types of semantic structure, like feature sharing or compositionality.

\section{Future Work}
An interesting avenue for future research in this line of work would be to examine the numerous other variants for finding sparse subnetworks.
Would they also separate? And if so, would they separate earlier or with better performance still?
Also, an investigation into the influence of things that worked well for lottery tickets, like learning rate schedules and resetting, as well as L1 or L2-regularisation.
Similar to the work in \autocite{BIMT}, other semantic structures of the data might be considered, like compositionality or weight sharing.
Finally, examine the methods on larger and more realistic datasets like CIFAR \autocite{cifar} or ImageNet \autocite{imagenet}, as well as translating the findings into convolutional neural net architectures.